Perceptions of Inequality and Meritocracy: Their Interplay in Shaping Preferences for Market Justice in Chile (2016-2023)

### 2025-07-28 resubmission/paper-resubmit.tex
Update varios ajustes

@@

\includegraphics[width=1\textwidth,height=\textheight]{blinded-paper-resubmit_files/figure-pdf/fig-alluvial-1.pdf}

@@

\includegraphics[width=1\textwidth,height=\textheight]{blinded-paper-resubmit_files/figure-pdf/fig-meanchange-1.pdf}

@@

\includegraphics[width=1\textwidth,height=\textheight]{blinded-paper-resubmit_files/figure-pdf/fig-interact-1.pdf}

>>>>

  \author{Juan Carlos Castillo}
            \affil{%
                  Departamento de Sociología, Universidad de Chile
              }
          \affil{%
                  Centro de estudios del conflicto y cohesión social
                  (COES)
              }
          \affil{%
                  Núcleo milenio de desigualdades y oportunidades
                  digitales (NUDOS)
              }
        \author{Andreas Laffert}
            \affil{%
                  Instituto de Sociología, Pontificia Universidad
                  Católica de Chile
              }
        \author{Kevin Carrasco}
            \affil{%
                  Centro de estudios del conflicto y cohesión social
                  (COES)
              }
        \author{Julio Iturra-Sanhueza}
            \affil{%
                  International Graduate School of Social Sciencies
                  (BIGSSS), University of Bremen, Germany
              }

@@

\includegraphics[width=1\textwidth,height=\textheight]{paper-resubmit_files/figure-pdf/fig-alluvial-1.pdf}

@@

\includegraphics[width=1\textwidth,height=\textheight]{paper-resubmit_files/figure-pdf/fig-meanchange-1.pdf}

@@

\includegraphics[width=1\textwidth,height=\textheight]{paper-resubmit_files/figure-pdf/fig-interact-1.pdf}
